An Efficient Calculus for Generalised Parikh Images of Regular Languages

### 2022-04-05 paper/main.tex
Work work

\usepackage{amsthm}
\usepackage{amsmath,mathtools,empheq,fancybox}
\usepackage{paralist}
\usepackage{url}
\usepackage{color}
\usepackage{textcomp,listings}
\usepackage{array}
\usepackage{mymacros}

@@

% Use a table!

@@

\section{Implementation and Experiments}

\contents{
\item length constraints
\item Parikh automata, automata with registers
\item Model-checking examples e.g. \cite{epistemic-logic}
}

@@

>>>>

\usepackage{amsthm}
\usepackage{amsmath,mathtools,empheq,fancybox}
\usepackage{paralist}
\usepackage{url}
\usepackage{color}
\usepackage{textcomp,listings}
\usepackage{array}
\usepackage{mymacros}
\usepackage{microtype}

@@

@@

\section{Implementation and Experiments}\label{sec:implementation}

We implement a calculus for Parikh automata as described in
Section~\ref{sec:parikh-automata}. The artefact submitted along with this paper
is a program that reads one or more products of one or more DFA, the
register incrementations performed along the edges of their transitions, and the
labels of the transitions as ranges of Unicode characters, along with a set of
constraints on the final values of their registers expressed as Presburger
arithmetic. We call this program \Catra{}.\footnote{If you really must read it
as an acronym, please read it as CAtegory Theory on Register Automata, or
alternatively if you find this whole paper to be too much of a theoretical
exercise as Can Anyone Think of A Real Application.}

\Catra{} is implemented in Scala, with the calculus described in this paper
implemented as a theory plug-in for the \Princess{} automated theorem
prover~\cite{princess}. For comparison, we also provide an implementation of the
baseline method from~\cite{generate-parikh-image}, a direct translation that
uses the~\Nuxmv{} symbolic model checker~\cite{nuxmv} to solve our constraints,
and \Fudge{the approximation described in~\cite{approximate-parikh}}. An example
of an input file \Fudge{illustrating every feature of the file format} can be
seen in Listing~\ref{lst:input-example}.

\contents{
  \item Listing: a nice input example
  \item Do we need to say any more about the nuxmv backend?
  \item Optimisations and tricks
}

In standard mode, supported by all back-ends, \Catra{} tries to satisfy the
constraints expressed by the input file, reporting satisfiable or unsatisfiable
much like traditional~SAT- or SMT solvers. Additionally, \Fudge{the baseline and} our own back-end also supports generating the Presburger formula describing the constraints of the input file \Fudge{using the method described in Section~\ref{}}

\subsection{\Catra{} is Versatile: Encoding Epistemic Logic Problems}

\contents{
\item Model-checking examples e.g. \cite{epistemic-logic}
}

\subsection{\Catra{} is Faster Than The Competition: Benchmarks and Their Results}

\contents{
\item length constraints
\item Parikh automata, automata with registers
\item Where do the instances come from!? Why?
\item Result table
\item Definition of winning
}

@@

\contents{
  \item Future extensions: more logics
  \item Loop invariants?
  \item Integration into string solvers?
}
